# Bringing the WDL Workflow to AnVIL

## Find the Workflow on Dockstore

Navigate to the Workflows tab of your Workspace. Select "Find a Workflow". 

```{r, fig.align='center', echo = FALSE, fig.alt= "", out.width = '100%'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1zUiupDXMZlZEIditsN5igggOim9qIrR9Ckf4N8fSAB8/edit#slide=id.g2794677b0ab_0_0")
```

When the dialog box opens, select "Dockstore" on the bottom left. This will take you to the Dockstore search page.

```{r, fig.align='center', echo = FALSE, fig.alt= "", out.width = '100%'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1zUiupDXMZlZEIditsN5igggOim9qIrR9Ckf4N8fSAB8/edit#slide=id.g2794677b0ab_0_5")
```

Enter fastq_subsample in the search box. Select the workflow "fhdsl/AnVIL_WDLs/fastq_subsample".

```{r, fig.align='center', echo = FALSE, fig.alt= "", out.width = '100%'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1zUiupDXMZlZEIditsN5igggOim9qIrR9Ckf4N8fSAB8/edit#slide=id.g2794677b0ab_0_16")
```

## Send the Workflow to AnVIL

On the right side "Launch with" menu, select "AnVIL". This will open a new tab.

```{r, fig.align='center', echo = FALSE, fig.alt= "", out.width = '100%'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1zUiupDXMZlZEIditsN5igggOim9qIrR9Ckf4N8fSAB8/edit#slide=id.g2794677b0ab_0_26")
```

Select the appropriate Workspace where you want the workflow to appear. Select "IMPORT".

```{r, fig.align='center', echo = FALSE, fig.alt= "", out.width = '100%'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1zUiupDXMZlZEIditsN5igggOim9qIrR9Ckf4N8fSAB8/edit#slide=id.g2794677b0ab_0_31")
```

You should now be back on AnVIL!